{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-24 paper.tex
Added performance graph

\section{Application Example}
\label{application}

@@

\subsection*{Architecture}

>>>>

\section{Performances and Application Example}
\label{application}

\subsection{Performances}
\label{performances}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{performances}
    \caption{Propagation times of one change (node creation)
    across $n$ worlds. The test is performed by running $n-1$ pass-through
    filters (independent processes) which each monitor one world and replicate
    any change into the next world. Times measured over 20 trials, performed on
    a 8 core machine.}
    \label{fig|performances}
\end{figure}

The main performance metric of \uwds is the \emph{propagation time}: the time is
take of a change in a given world to cascade to all the dependant

\subsection{Application to service robots and human-robot interaction}

@@

\subsection{Architecture}
